Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-03 paper.tex
Update until subpagraph 3

{\color{magenta}
It is worth mentioning that experimental dielectric results of 2D
materials generally need to define an ``effective thickness'' of the sheet
to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
extract information for the real part of the dielectric functions.  We
argue that such procedure may induce inevitably variations of the
results as the thickness is normally chosen by the interlayer spacing
of the respective bulk materials (see Supplementary Section
\ref{SI-sec:2D-3D-rescale}).
}
%
%%%
%
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
%.
%
%
%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 
%

To solve the problem described above, we need to find the
$L$-independent alternative of $\varepsilon_{\mathrm{SL}}$, which is
related to both electrostatic and optical properties of a 2D
material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
with $L$, we obtain the sheet polarization density that is,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, in
direction $p$. Following the discussion in the previous section,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of lattice
size when $L$ is large enough, due to the saturation of
$\boldsymbol{u}^{p}$.

@@

Similar to the molecular polarizability \cite{Israelachvili_2011}, we
can define a 2D electronic polarizability $\alpha_{\mathrm{2D}}$ which
characterizes the ability to induce dipole moment of a 2D material. It
is associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
\alpha_{\mathrm{2D}}^{pq} \boldsymbol{E}_{\mathrm{loc}}^{q}$
\cite{T_bik_2004}, where $\boldsymbol{E}_{\mathrm{loc}}$ is the local
electric field causing the polarization. At $L \rightarrow \infty$
limit, $E_{\mathrm{loc}}$ can be solved using electrostatic boundary
conditions of slab geometry \cite{Markel_2016}. The continuity of the
electric field along the in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$,
while for the out-of-plane component, the dipole screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}, where
$\boldsymbol{E}^{\parallel}$ and $\boldsymbol{E}^{\perp}$ are the
external field in the in-plane and out-of-plane directions,
respectively. Combining with Eqs. \ref{eq:def-eps-1} and
\ref{eq:def-eps-2},
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
can be related with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:

@@

  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
% 20191003-16:00
% As pointed before, as we limit the discussion on electronic contributions to the dielectric properties, $\alpha_{\mathrm{2D}}$ characterizes the polarizability of electron cloud of a 2D materials.
% refers to the electronic polarizability (the polarizability of the
% electron cloud \cite{Israelachvili_2011}).
{\color{magenta} We also note that such
approach is essentially different from the effective medium theory
\cite{Aspnes_1982,Markel_2016} (EMT) treatment of 2D materials, in
which the hypothetical effective dielectric constant of 2D materials
$\varepsilon_{\mathrm{2D}}$ are extracted from the macroscopic
dielectric constant \cite{Matthes_2016,Laturia_2018}, from
pre-determined 2D layer thickness $\delta$. The 2D electronic
polarizability approach solves the issue of overestimation in the EMT
approach, and $\alpha_{\mathrm{2D}}$ has an umambiguous physical
meaning. Detailed discussions about the different between the 2D
polarizability and the EMT approach, can be found in Supplementary
Section \ref{SI-sec:2D-3D-rescale}.
}

@@

Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
{\color{red} Convergence plot in SI} Such result is in good agreement
with the spatially localized induced dipole moment of a 2D materials
as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Fig.\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Fig. \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

@@

>>>>

@@

%%%
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
%.

@@

%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 

@@

To solve the problem described above, we need to find the
$L$-independent alternative of $\varepsilon_{\mathrm{SL}}$, which is
related to both electrostatic and optical properties of a 2D
material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
with $L$, we obtain the sheet polarization density that is,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, in
direction $p$. Following the discussion in the previous section,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of lattice
size when $L$ is large enough, due to the saturation of
$\boldsymbol{u}^{p}$.
%
Similar to the molecular polarizability \cite{Israelachvili_2011}, we
can define a 2D electronic polarizability $\alpha_{\mathrm{2D}}$ which
characterizes the ability to induce dipole moment of a 2D material. It
is associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
\alpha_{\mathrm{2D}}^{pq} \boldsymbol{E}_{\mathrm{loc}}^{q}$
\cite{T_bik_2004}, where $\boldsymbol{E}_{\mathrm{loc}}$ is the local
electric field causing the polarization. At $L \rightarrow \infty$
limit, $E_{\mathrm{loc}}$ can be solved using electrostatic boundary
conditions of slab geometry \cite{Markel_2016}. The continuity of the
electric field along the in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$,
while for the out-of-plane component, the dipole screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}, where
$\boldsymbol{E}^{\parallel}$ and $\boldsymbol{E}^{\perp}$ are the
external field in the in-plane and out-of-plane directions,
respectively. Combining with Eqs. \ref{eq:def-eps-1} and
\ref{eq:def-eps-2},
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
can be related with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
% 20191003-16:00
% As pointed before, as we limit the discussion on electronic contributions to the dielectric properties, $\alpha_{\mathrm{2D}}$ characterizes the polarizability of electron cloud of a 2D materials.
% refers to the electronic polarizability (the polarizability of the
% electron cloud \cite{Israelachvili_2011}).

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
{\color{red} Convergence plot in SI} Such result is in good agreement
with the spatially localized induced dipole moment of a 2D materials
as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Fig.\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Fig. \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

\subsection{Comparison with effective dielectric model}
\label{sec:comp-with-effect}

Apart from the 2D electronic polarizability proposed here, it is worth
mentioning that a widely-used approach in literature is to treat the
2D material as a slab with an effective dielectric tensor
$\varepsilon_{\mathrm{2D}}$ and thickness $\delta_{\mathrm{2D}}$. Such
method can be found in both experimental and theoretical studies, such
as to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance /
transmission spectra \cite{Li_2014, Yoffe-Wilson69}, optical
conductance \cite{Matthes_2016} and many-body interactions
\cite{Sohier_2016,Meckbach_2018} of 2D materials. The effective
dielectric model allowing applying physical laws of bulk systems
directly to 2D materials using $\varepsilon_{\mathrm{2D}}$. However,
there are several drawbacks of such approach, first of all, the
wavevector($q$)-dependency of dielectric screening in 2D
sheets~\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Trolle_2017_eps_subst}
is not captured. More severely, here we show that, due to the
uncertainty of $\delta_{\mathrm{2D}}$, the calculated
$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
is extremely sensitive to the choice of $\delta_{\mathrm{2D}}$, making
such model questionable.

The basic assumption of the effective dielectric model (EDM) can be
seen in Figure~\ref{fig-emt}\textbf{a}, where the macroscopic
$\varepsilon_{\mathrm{SL}}$ is considered to be contributed by (i) a
2D slab with effective dielectric constant $\varepsilon_{\mathrm{2D}}$
and thickness $\delta_{\mathrm{2D}}$ and (ii) vacuum spacing with
distance $L-\delta_{\mathrm{2D}}$. Using the effective medium theory
(EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between
$\varepsilon_{\mathrm{SL}}$ and $\varepsilon_{\mathrm{2D}}$ can be
expressed using capacitance-like
equations~\cite{Matthes_2016,Laturia_2018} :
\begin{subequations}
  \begin{eqnarray}
    \label{eq:emt-1}
    {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}\\
     \label{eq:emt-2}
    {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \frac{1}{\varepsilon_{\mathrm{2D}}^{\perp}} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}
  \end{eqnarray}
\end{subequations}
In principle, both the values of $\varepsilon_{\mathrm{2D}}$ and
$\delta_{\mathrm{2D}}$ are unknown for a certain 2D material. To
minimize the modeling error, we used non-linear least-square fitting
to extract $\varepsilon_{\mathrm{2D}}$ and $\delta_{\mathrm{2D}}$ of
selected 2H TMDCs simultaneously from \textit{ab initio}
$\varepsilon_{\mathrm{SL}}$ -- $L$ data in
Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{b} (details see
Supplementary Figure~\ref{SI-fig:rescale-prb}). The fitted values of
the slab thickness, $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$
and $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ from in-plane and
out-of-plane data, respectively, are shown in Supplementary
Table~\ref{SI-tab:delta-L-DFt}. As seen in Figure
\ref{fig-emt}\textbf{b}, the estimation error of the thickness
estimated from different directions is around 0.06$\sim{}$0.27
\AA{}. Although such uncertainty only corresponds to about
1$\sim{}$4\% of the interlayer spacing in the bulk counterparts of
these 2D materials, its influence on the calculated values
$\varepsilon_{\mathrm{2D}}^{\parallel}$ and
$\varepsilon_{\mathrm{2D}}^{\perp}$ is significant. We estimated the
dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta_{\mathrm{2D}}$ deviates
from the best fitted value by $\pm{}$2.5 \AA{}, as shown in Figures
\ref{fig-emt}\textbf{c} and \ref{fig-emt}\textbf{d},
respectively. $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
with $\delta_{\mathrm{2D}}$ with a uncertainty of $\sim{}$10\%, while
strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans over
more than one order of magnitude. The sensitivity of
$\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta_{\mathrm{2D}}$ explains
the discrepancy in literature that both isotropic~\cite{Sohier_2016}
and highly anisotropic~\cite{Matthes_2016,Laturia_2018}
$\varepsilon_{\mathrm{2D}}$ tensors for 2D materials under the EDM are
reported. As a consequence, the estimated values of
$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
is highly questionable.

On the contrary, the proposed $\alpha_{\mathrm{2D}}$ approach does not
suffer from such deficiencies, despite its relatively simple
formalism. The relative uncertainty of $\alpha_{\mathrm{2D}}$ is
generally at the order of 10\textsuperscript{-4} (Supplementary Figure
{\color{red} XX}). In addition, the calculation of
$\alpha_{\mathrm{2D}}$ technically simpler than
$\varepsilon_{\mathrm{2D}}$: (i) $\alpha_{\mathrm{2D}}$ can be
achieved using single-point calculation of macroscopic dielectric
tensor, while $\varepsilon_{\mathrm{2D}}$ requires non-linear fitting
of multiple $\varepsilon_{\mathrm{SL}}$ -- $L$ data points; (ii) the
values of $\alpha_{\mathrm{2D}}$ typically converge well for large $L$
($>$20 \AA{}), while $\varepsilon_{\mathrm{2D}}$ suffers from the
uncertainty as described above.

@@

\subsection{Universal scaling laws of $\alpha_{\mathrm{2D}}$}
\label{sec:univ-scal-laws}
